---
title: "Major Assignment, Part 2"
author: "FIRSTNAME LASTNAME"
date: "January 21, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Exploration

### Research Question

State your research question in words

### Data source, and description of variables

Describe your data source, and describe each variable

> line by line okay

# Begin exploration
 
### Data pre-load

```{r preload, include=TRUE}
library(tidyverse)
library(lubridate)

source("../R/6003Functions.R")

mydata <- read.csv("../data/MYDATA.csv") 

# PASTE ALL CODE ASSOCIATED WITH LOADING AND CLEANING DATA HERE (i.e. from 001_DataSetup.R)


```

State in words if you made any decisions to exclude or alter data, based on what you discovered in your pre-load. 


### 1. Outliers Y and X

Are there outliers in Y or X?

Y: Stage

```{r outliersY}
plot()
```

X: length, age, date, maturity

```{r outliersX}
plot()

dotchart()
```

DESCRIBE HERE

### 2. Homogeneity Y

Check Y against categorical X's. 

```{r homogeneity}
p <- ggplot(data=, aes(x=, y=)) +
  geom_boxplot() #Apply faceting if needed 
p
```

DESCRIBE HERE: IS THERE HETEREOGENEITY OR IS Y HOMOGENOUS ACROSS CATEGORICAL X?

### 3. Normality  Y

Check distribution of Y for normal distribution

```{r normality}
p <- ggplot(data=, aes(x=)) +
  geom_histogram(binwidth = 1)
p 

# OR hist()
```

DESCRIBE WHAT YOU SEE

**If it's not normal, is it explainable by another covariate?**

*hint: plot distributions at each level of categorical covariate*

```{r normality2}
p <- ggplot(data=, aes(x=)) +
  geom_histogram(binwidth = 1) + facet_wrap(~)
p 
```

### 4. Zero trouble Y 

Are there many zero values of Y?

```{r zerotrouble}
plot(table()) 

# Anything where students are showing absence of zeroes works here
```

DESCRIBE: ARE THERE MANY ZEROES?

### 5. Collinearity X 

Is there collinearity among covariates?

```{r collinearity}
pairs(~  +  +  + , 
      lower.panel=panel.smooth, upper.panel=panel.cor, 
      data=) 

#Students should put all covariates in this
```

WHAT COVARIATES ARE COLINEAR?

ARE THERE ANY OBVIOUS NON-LINEAR RELATIONSHIPS?

### 6. Relationships Y and X

Plot all covariates against Y

```{r relationships}

p <- ggplot(data=, aes(x=, y=)) + geom_point()
q <- ggplot(data=, aes(x=, y=)) + geom_point()
r <- ggplot(data=, aes(x=, y=)) + geom_boxplot() #Use appropriate plot types
s <- ggplot(data=, aes(x=, y=)) + geom_point()

multiplot(p,q,r,s, cols = 2)
```

DESCRIBE RELATIONSHIPS PRESENTED IN EACH PLOT

### 7. Interactions

Is relationship between covariates and Y mediated by categorical covariates?

*hint: You need at least two categorical covariates to look for an interaction.*

```{r interactions}
#coplot(Y ~  | BLANK * BLANK, #insert categorical covariates on right side of |
#       data=,
#       panel=function(x,y,...) {
#         panel.smooth(x,y,span=0.8,iter=5,...)
#         abline(lm(y ~ x), col="blue") } )


```

WERE ANY INTERACTIONS OBSERVABLE?

### 8. Independence Y

Are there any reasons to suspect non-independence of observations? Most common would be due to *repeated measures*, *spatial autocorrelation*, or *temporal autocorrelation*. 

Is there a nested structure to the data?

DESCRIBE HERE.

### Recap

Re-state what you found, and what decisions you made

1. Outliers Y and X: 
2. Homogeneity Y: 
3. Normality Y: 
4. Zero trouble Y: 
5. Collinearity X:
6. Relationships Y and X: 
7. Interactions: 
8. Independence Y: 


