---
title: "Major Assignment Part 3 Template"
author: "FIRSTNAME LASTNAME"
date: "xxx"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 3

This is a template to help you copmlete Part 3 of the major assignment. Here you will complete each step as articulated in https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.12577

## Data pre-load

Here is a block of space to paste in any code needed to load the data. For Part 3, I do not need to see your pre-load code.

```{r preload, echo=FALSE, results="hide", include=FALSE}
library(tidyverse)
library(lubridate)

source("../R/6003Functions.R")

x <- read.csv("") 
```

## Research Question

*Re-state your research question here*

### 1. Identify the dependency structure in the data 

*State, in words, if dependency structure exists in your data. If there is no structure, explain why you believe each replicate to be truly independent. You may re-insert your study diagram from Part 2 here to help*

### 2. Present the statistical model

*For mathematical notation in Markdown, please see: https://csrgxtu.github.io/2015/03/20/Writing-Mathematic-Fomulars-in-Markdown/* 

*Write the model formula. Remember we need to see a distribution a link function and a predictor function*.

See the example below: 

**Distribution**
$NumCatch_{ij} = P(\mu_{ij})$
$E(NumCatch_{ij}) = \mu_{ij}$

**Link function**
$\eta_{ij} = log(\mu_{ij})$

**Predictor function**
$\eta_{ij} = \beta_1Temperature_{ij} + TrapType_{ij} + StudyDay_i$
$StudyDay_i ~ N(0, \sigma^2_{StudyDay})$


### 3. Fit the full model

** Are you going to standardize covariates? Why or why not? **

```{r ModelPrep, echo=FALSE, include=FALSE}
# Input any code here that will PREPARE THE DATA for model fitting. 
# Note I've masked it above - I don't need to see this bit :)
```


```{r FitModel}
# Input any code here for model fitting. I *do* need to see this bit.

m <- glmer(NumCatch ~ Temperature + Traptype + (1 | StudyDay))

summary(m)
```


### 4. Validate the full model

**QUESTION: Have you satisfied conditions of independence and fixed X?**

Here are a few validation steps. Note that the steps needed depend on the model you fit. Please include only those that are necessary and remove the rest:

#### Normality of residuals

```{r Normality}
hist(resid(MYMODEL, type="pearson"))
```

**Are residuals normally distributed?**

#### Overdispersion: 
```{r Overdispersion}
E1 <- resid(MYMODEL, type = "pearson")
N  <- nrow(MYDATA) #Replace MYDATA with your dataset
p  <- length(coef(MYMODEL)) #Replace MYMODEL with your model
sum(E1^2) / (N - p) 
```

*Is your model overdispersed?*


*If yes, please explore potential reasons:*

A. Outliers Y
B. Missing covariates?  
C. Missing interactions?
D. Zero inflation?     
E. Dependency?     
F. Non-linear patterns  
G. Wrong link function   

*What actions do you intend to take to rectify overdispersion?*

#### Residuals 

**Interpret each of the following:**
```{r ResidVsFit}
#Plot residuals vs. fitted values

```

```{r ResidVsFit}
#Plot residuals vs. covariates in the model

```

```{r ResidVsFit}
#Plot residuals vs. covariates not in the model
```

```{r ResidVsFit}
#Plot residuals vs. time and space
```


**Question: Do you intend to engage in a model selection procedure? If so, what procedure will you follow? Why or why not?**

### 4A. Model-selection and re-validation

** Show any model selection procedure you used, then re-validate and present your reduced model **



### 5. Interpret and present numerical output of the model

```{r PresentOutput}
summary(MYMODEL) #replace MYMODEL with your model
```

** Optional bonus: format this output as a nice publication-quality table (https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html)**

** Write out sentences in plain English that interpret your key findings, as related to the research question you stated in step 1 **


### 6. Create a visual representation of the model

** See: https://pbreheny.github.io/visreg/**

```{r visualize}
# Use the visreg package, or ggpredict
# See Week 9 R code with some exmaples
```

WHAT COVARIATES ARE COLINEAR?

ARE THERE ANY OBVIOUS NON-LINEAR RELATIONSHIPS?

### 7. Simulate from the model

** Check for zero-inflation**
```{r simluate}
# Simulation to establish zero-inflation
N <- nrow(MYDATA) #MYDATA
gg <- simulate(MYMOD, 10000) #MYMOD 

zeros <- vector(length = 10000)
for (i in 1:10000){
  zeros[i] <- sum(gg[,i] == 0) / N
}

par(mar = c(5,5,2,2), cex.lab = 1.5)
plot(table(zeros), 
     xlim = c(0, 0.05),
     axes = FALSE,
     xlab = "Percentage of zeros",
     ylab = "Frequency")
axis(2)
axis(1, at = c(0.01, 0.02, 0.03, 0.04, 0.05),
     labels = c("1%", "2%", "3%", "4%", "5%"))     
points(x = sum(MYDATA$MYRESPONSEVARIABLE==0) / N, y = 0, pch = 16, cex = 5, col = 2) #MYDATA and MYRESPONSEVARIABLE

```

** Was there zero-inflation? If yes, what might you try next? (You don't have to actually do it for Part 3)**

# All done! I hope you enjoyed FISH 6003
